Evolutionary stretegies

### 2016-01-23 evolutionaryComputation/summery.tex
added about pop sizing

>>>>

\subsection{Rank based selection}
Proporitionate selection has not a constant selection pressure.

\section{Population sizing}
Selection viewed as descision making proscess withing partitions:
schama competition. When best schema looses comptetition we have a 
selection descision error. The amount of decision errors that
can be afforded at a given pop size can be explained by random walks.
\subsection{Selection error}
Probablity selection error is equal to the probablity that the best schema is represented
by a string with fitness less than the representative worst schema. wich is also equal
to the probability that the fitness difference is nagative.
%TODO: add fancy pants maths.

\subsection{Random walks}
One dim space of size $N + 1$. A particle in above
space in postition $x\in \{0,\dots,N\}$. The particle can move
left with probability $p$ and right with probability $1-p$.
when the particle reaches the boundries the walk ends.
$P_N(x)$ the probability that the particle is absorbed
by boundry $N$. When it currently is at pos $x$.
Diff equation:
$P_N(x)=pP_N(x+1)+(1-p)P_N(x-1)$

\subsection{Population sizing \& gambler's ruin}
The number of optimal bit values `1' in the population at a certain
position. - this is, for the partition considered - corresponds
to the position $x$ in the gambler's ruin model.
The boundries correspond to all bit vlaues in the population being
equal to a bit value. WHen the boudaries are reached the random walk
ends. The proba bility that the amount of optoimal string values in the
population at the partition is increased by one is equal to the probability
that the selection decision making is correct for that partition. This
corresponds to the probability that the particle moves to the right(p).
Desired convergence corresponds to the particle reaching the $x=N$ boundary.
Premature convergence - this is, loosing the optimal bit value in the
population - correspons the the particle reaching the $x=0$ boundary.
$P[OptConv]=\frac{1-(\frac{P[SellErr]}{1-P[SellErr]})^{N/2}}{1-(\frac{P[SellErr]}{1-P[SellErr]})^N}
\approx 1-(\frac{\sqrt{\pi l}-2}{\sqrt{\pi l}+2})^{N/2}$
Critical pop size: $N \approx ln(1-P[OptConv]\frac{\sqrt{pi l}}{-2}$
